### 2014-03-19 msc-thesis/chapters/3/sec-iced.tex
MSC final edits

\subsection{Threats to Validity}
Because of the exploratory nature of this work, I chose Grounded Theory as my research method, which has some implications regarding the
limitations and threats to validity of this study. While I achieved high saturation regarding the topics focused on in this study, other
populations studied from outside of this studies participants may add new insights into the pool of findings. As a result of this, findings
from this study may not relate to everyone or generalize to outside of the group of participants involved in this study.

@@

My findings have indicated that:
indirect conflicts occur frequently and are likely caused by software contract changes;
while design by contract, add and deprecate, and personal experience help prevent indirect conflicts,
developers tend to prefer to use detection and resolution processes or tools
over those of prevention, and developers want indirect conflict tools to focus on automatic debugging and better source code analysis.

>>>>

\subsection{Threats to Validity}
Because of the exploratory nature of this work, I chose Grounded Theory as my research method, which has some implications regarding the
limitations and threats to validity of this study. While I achieved high saturation regarding the topics focused on in this study, other
populations studied from outside of this studies participants may add new insights into the pool of findings. As a result of this, findings
from this study may only relate to developers or managers from the projects I studied.

@@

In addresses the three issues of scalability, false positives, and information overload, my findings indicate:
indirect conflicts occur frequently and are likely caused by software contract changes;
while design by contract, add and deprecate, and personal experience help prevent indirect conflicts,
developers tend to prefer to use detection and resolution processes or tools
over those of prevention, and developers want indirect conflict tools to focus on automatic debugging and better source code analysis.

### 2014-03-19 msc-thesis/chapters/5/chapter-conclusion.tex
MSC final edits

Through the analysis in Chapter 4, I have shown the disjoint of current awareness understanding versus the practical
awareness needs found in industry. This disjoint, caused by the difference of academic and practical understanding in awareness needs,
ultimately led to tools with information overload and false positive issues. This was quite evident from my tool Impact as
presented in Study 2. Even when the tool is based around the statistical results of Study 1, the disjoint between what academics
determine developers want versus what they themselves want is quite obvious. The debate of prevention versus cure has been presented along with
the industrial tendency towards curative measures. However, while a curative approach may be favored by developers, further research is needed
to fully assess the positive and negative influences of prevention versus cure for productivity and quality concerns. Finally, I have shown
the gap of analytical evolution tools needed for dependency identification and indirect conflicts. This gap, unless addressed, may prevent
future industrial adoption of tools produced by researchers for lack of fit in industrial needs. While, I have shown a potential solution to address
a fraction of the analysis gap through contextual patterns of indirect conflicts, many other problems of the analysis gap remain problems
for future research.

>>>>

Through the analysis in Chapter 4, I have shown the disjoint of current awareness understanding versus the practical
awareness needs found in industry. This disjoint, caused by the difference of academic and practical understanding in awareness needs,
ultimately led to tools with information overload and false positive issues. This was quite evident from my tool Impact as
presented in Study 2. Even when the tool is based around the statistical results of Study 1, the disjoint between what academics
determine developers want versus what they themselves want is quite obvious. The debate of prevention versus cure has been presented along with
the industrial tendency towards curative measures. However, while a curative approach may be favored by developers, further research is needed
to fully assess the positive and negative influences of prevention versus cure for productivity and quality concerns. Finally, I have shown
the gap of analytical evolution tools needed for dependency identification and indirect conflicts. This gap, unless addressed, may prevent
future industrial adoption of tools produced by researchers for lack of fit in industrial needs. While I have shown a potential solution to address
a fraction of the analysis gap through contextual patterns of indirect conflicts, many other problems of the analysis gap remain problems
for future research.
